---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19tracker

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-xhee0013/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-xhee0013/actions)
<!-- badges: end -->

The goal of covid19tracker is to interactively visualize the situation of COVID-19 cases in three countries from January to September and provide a platform for performing and reviewing the change of cases distribution for each regions in all countries.

## Installation

You can install the released version of covid19tracker from [Github](https://github.com/etc5523-2020/r-package-assessment-xhee0013) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-xhee0013")
```
## Data collection

The data set with COVID-19 information is provided by `coronavirus` package which is from which is from [RamiKrispin GitHub repo](https://github.com/RamiKrispin/coronavirus).

This package contains two data sets: `covid19_count` and `covid19_region`

- **covid19_count**: This data set displays the monthly coronavirus cases in each country with each region in each country

- **covid19_region**: This data set shows the cumulative COVID19 confirmed cases for each region in three countries.


## Package Functions

This package provides three function to use:

- **launch_app**: This function runs the COVID-19 Tracker Shiny App exploring the case situation of Coronavirus for each region in three countries

- **summary_table**: This function create a styled and formatted table to represent the summary case situation of COVID19 in each country.

- **input_option**: This function provides the shiny input options for the different variables which are contained in the data sets.

## Example

This is a basic example to show both data sets in this package:
```{r country}
library(covid19tracker)
library(tibble)
covid19_count
```

```{r region}
covid19_region
```

### The overall time series trend of COVID-19 case 

```{r lineplot,warning=FALSE, message=FALSE}
library(tidyverse)

covid19_count%>%
  dplyr::filter(province=="Hubei")%>%
  ggplot(aes(x=Month,y=Cases,col=Type))+
  geom_line()+
  geom_point()+
  labs(x = "Month", y = "Cases count", title = "Hubei")+
  theme_bw()+
  theme(legend.position="bottom",
        legend.direction="horizontal",
        legend.box.background = element_rect(fill = "transparent"),
        legend.background = element_rect(fill ="transparent",linetype="solid",color = "#BDD9EC"),
        axis.text = element_text(size = 10),
        legend.text = element_text(size = 10),
        legend.title = element_blank(),
        axis.title = element_text(size = 12),
        axis.line = element_line(size = 0.4, colour = "white"),
        plot.background = element_rect(fill = "#e3f0fc"),
        panel.background = element_rect(fill="transparent"),
        panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.ticks.x.bottom = element_line(colour = "white",size = 0),
        plot.margin = margin(10,20,10,20))+
  scale_x_continuous(breaks = seq(1, 9,1))

```

