---
title: "Explore the case situation of COVID19 via Shiny Application in three countries"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Explore the case situation of COVID19 via Shiny Application in three countries}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(covid19tracker)
```
This `covid19tracker` package provides some function and cleaned data for describing how an Shiny web application could be launched interactively, and giving the visualization about the COVID19 case situation.

## Loading package
The `covid19`tracker package can be installed directly from [GitHub](https://github.com/etc5523-2020/r-package-assessment-xhee0013) with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("eetc5523-2020/r-package-assessment-xhee0013")

# load the package
library(covid19tracker)
```


## Loading the data sets

This package also contains the following data sets:

- **covid19_count**: This data set displays the monthly coronavirus cases in each country with each region in each country
- **covid19_region**: This data set shows the cumulative COVID19 confirmed cases for each region in three countries.
```{r data, eval=FALSE}
covid19_count
covid19_region
```

## Main function

The main functions in this package includes:

- **summary_table**: This function create a styled and formatted table to represent the summary case situation of COVID19 in each country.
```{r table}
summary_table("China")

```


- **input_option**: This function provides the shiny input options for the different variables which are contained in the data sets. In this case, the countries in `covid19_count` will be displayed such as Australia,China or United Kingdom.

```{r,eval=FALSE}
input_option("country", covid19_count)
```


## Launching the Shiny App

When downloading the package, the shiny app can be launched using the following `launch_app` function.

```{r launch, eval=FALSE}
launch_app()
```


The main motivation of this simple shiny app is designed to interactively visualize the situation of COVID-19 cases in three countries such as Australia, China and United Kingdom from January to September and provide a platform for performing and reviewing the change of cases distribution for each regions in all countries across time. All data used by this application are collected through `coronavirus`package which is from [RamiKrispin GitHub repo](https://github.com/RamiKrispin/coronavirus). The coronavirus dataset consists of measurements of case distribution between countries and regions across time, therefore it will be used and constructed a series of analysis to evaluate the situation of COVID-19 pandemic.

In addition,the four main visualization sections are contained in the application:   

1. A leaflet map displaying the confirmed case of COVID-19 in each region with its corresponding country.

2. A time series line plotly graph showing the time series data about how the three type of COVID-19 cases such as confirmed, death and recovered distributed from January to September in each corresponding region.

3. A pie plotly graph representing the proportion of each case type in different months in each specific region.  

4. A table recording the number of confirmed,death and recovered case in each country from January to September

Furthermore, there is an `About` tab to explain more details about the introduction and output of this COVID-19 Tracker shiny app. This is to give the user more clearly understanding about how to use this shiny app, and the illustration of each output.

More detailed instructions on how to use the applications and its content are provided on the [remote host](https://xitong-he.shinyapps.io/shiny-assessment-xhee0013).

## Further comment
If you would like to contribute to the package or leave comments, please feel free to leave an [issue on Github](https://github.com/etc5523-2020/r-package-assessment-xhee0013/issues) or send me an email via xhee0013@student.monash.edu
